\documentclass[12pt]{article}

% Cahiers wants Times New Roman:

\usepackage{times}

% Cahiers wants this page layout:

\usepackage[a4paper,text={128mm,185mm}, centering]{geometry}

\usepackage{changepage}
% Slight modification of section titles (optional):

\usepackage{titlesec}

\titleformat{\section}[hang]%
{\bfseries\large}{\thesection.}{1ex}{}%

\titleformat{\subsection}[hang]%
{\bfseries}{\thesubsection}{1ex}{}%

\usepackage{amsmath, amsthm}
\usepackage{fancyhdr}
\pagestyle{fancy}


%lefthead and rightheads: authors and short title
\lhead{\sc\bfseries R.K. $\&$ A.M-M.}
\rhead{\sc\bfseries An $E_\infty$-structure on cubical cochains}

%title
\title{\vskip 5pt  \bf  \textsc{A combinatorial $E_\infty$-algebra structure on cubical cochains and the Cartan--Serre map}}
% Nota Bene : please, write your title in capital letters, as in the example here.
%authors
\author{
	\itshape\bfseries {Ralph~M.~Kaufmann} \and
	\itshape\bfseries {Anibal~M.~Medina-Mardones}
}

\input{aux/style}
\input{aux/usualcmds}
\addbibresource{aux/usualpapers.bib}
\addbibresource{aux/mypapers.bib}
\usepackage{csquotes}
\input{aux/commands} % new cmds here
\addbibresource{aux/bibliography.bib} % new bibs here
\input{aux/figures}

\begin{document}
	\maketitle
	%Nota bene:  the next two commands erase pages numbers (the right page numbers will be add by the editors on the pdf)
	\cfoot{}
	\thispagestyle{empty}
	%%
	\vskip 25pt
	% Abstract in French and in English, followed by Keywords and MSC:
	\begin{adjustwidth}{0.5cm}{0.5cm}
		{\small
			{\bf R\'esum\'e.} Les cochaînes cubiques sont munies d'un produit associatif, dual à la diagonale de Serre, relevant la structure commutative graduée en cohomologie.
			Dans ce travail, nous introduisons par des méthodes combinatoires explicites une extension de ce produit à une structure $E_\infty$.
			Comme application, nous prouvons que l'application de Cartan--Serre, qui relie les cochaînes singulières cubiques et simpliciales d'espaces, est un quasi-isomorphisme de $E_\infty$-algèbres. \\
			{\bf Abstract.} Cubical cochains are equipped with an associative product, dual to the Serre diagonal, lifting the graded commutative structure in cohomology.
			In this work we introduce through explicit combinatorial methods an extension of this product to a full $E_\infty$-structure.
			As an application we prove that the Cartan--Serre map, which relates the cubical and simplicial singular cochains of spaces, is a quasi-isomorphism of $E_\infty$-algebras. \\
			{\bf Keywords.} Cubical sets, cochain complex, cup product, Cartan--Serre map, $E_\infty$-algebras, operads. \\
			{\bf Mathematics Subject Classification (2020).} 55N45, 18M70, 18M85.
		}
	\end{adjustwidth}

	% Content
	\input{sec/introduction}
	\input{aux/acknowledgment}
	\input{sec/preliminaries}
	\input{sec/props}
	\input{sec/action}
	\input{sec/comparison}

	% Bibliography
	\sloppy
	\printbibliography

	% Addresses
	\noindent \textit{Ralph M. Kaufmann} \\
	Purdue University \\
	\href{mailto:rkaufman@purdue.edu}{rkaufman@purdue.edu} \\
	\newline
	\noindent \textit{Anibal~M.~Medina-Mardones} \\
	Max Plank Institute for Mathematics and University of Notre Dame \\
	\href{mailto:ammedmar@mpim-bonn.mpg.de}{ammedmar@mpim-bonn.mpg.de}
\end{document}